\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\name{Sreehari}{Pulickamadhom Sreedhar}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}\textbf{Policy Analysis and Economics}\end{center}
\begin{center}
\begin{tabular}{ c c c }
\faMobile\enspace +61 450087293 & \enspace\enspace spulickamadhom@gmail.com & \enspace\enspace\faHome\enspace Canberra, ACT
\end{tabular} \\
\begin{tabular}{c c}
\faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/sreehari-sreedhar/}{in/sreehari-sreedhar} &
\enspace\enspace\faGithub\enspace \color{blue} \href{https://github.com/orectique}{github.com/orectique}
\end{tabular}
\end{center}

\section{Profile}
{I stand at the intersection of rigorous policy analysis and data science, employing intricate microsimulation models to explore variations in human behavior in response to policy interventions. My academic pursuits have encompassed studying the distributional effects of Australian tax cuts and mapping the spatial scope of social unrest, revealing patterns embedded within complex datasets. Through research work at ALGA, Mandala Partners and QuantEcon, I have honed my analytical skills and cultivated a collaborative spirit. Now, with a proven track record of leading data analysis teams, I seek to apply my expertise to pressing policy challenges, leveraging data to inform actionable strategies.}

\section{Areas of Expertise}
{Agent-Based Modelling - Policy Analysis - Microsimulation - Negotiation and Mediation - Statistical Analysis and Modelling - Machine Learning}

\section{Professional Experience}
\customcventry{06/2024 ‐ Present}{{\color{blue}\href{https://alga.com.au/}{(Australian Local Government Association)}}}{Modeller - Junior Policy Advisor,}{Canberra, ACT}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]  
 \item Created a knowledge base of data and modelling tools relevant to local government.
 \item Collaborated with Policy Directors to generate quick analyses on portfolios such as climate adaptation and Commonwealth grants.
\end{itemize}}}

\customcventry{09/2023 ‐ 12/2023}{{\color{blue}\href{https://mandalapartners.com/}{(Mandala Partners)}}}{Research Intern,}{Canberra, ACT}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Reviewed comparative policy research to study the impact of federalism in Australian states and territories.
\item Engineered estimates of indicators of quality of life, education, and healthcare through multifactor analyses and statistical modeling.
\item Collaborated with partners, analysts, and engagement managers to streamline quantitative report generation. 
\end{itemize}}}

\customcventry{07/2023 ‐ 12/2023}{{\color{blue}\href{https://quantecon.org/}{(QuantEcon@ANU)}}}{Research Assistant,}{Canberra, ACT}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Gained hands-on experience in the use of high-performance computing and dynamic programming approaches to classical economics problems.
\item Co-authored and reviewed material in the QuantEcon lecture series authored by Prof. Thomas Sargeant (NYU) and Prof. John Stachurski (ANU). 
\item Instructed a QuantEcon Lunch Workshop on the use of multidimensional weighting and constrained sampling in the context of spatial microsimulations of the Australian taxed population.
\end{itemize}}}

\customcventry{10/2021 ‐ 05/2022}{{\color{blue}\href{https://www.amrita.edu/}{(Amrita Vishwa Vidyapeetham)}}}{Lead Data Analyst,}{Coimbatore, TN}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Analyzed sociological data from survey conducted as part of a joint project between the Dept. Of Food and Nutrition and Dept. of Science and Technology, Government of India.
\item Developed an analytical tool to summarize and analyze semi-structured geospatial data, designed to be intuitive for use by non-technical social scientists.
\item Trained field researchers in ethical data usage and the analysis of deidentified survey data.
\end{itemize}}}

\customcventry{04/2021 ‐ 06/2021}{{\color{blue}\href{https://math.mit.edu/directory/profile.html?pid=1521}{(Dr. Peter J. Kempthorne, MIT)}}}{Research Intern,}{Remote}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Engaged in methodic analysis and aggregation of ACLED social unrest data to study spatial distributional variation of protest frequency.
\item Introduced a new measure of unrest severity using measures of perceived violence and proposed a novel way to map and compare periods of social unrest using latent measures of severity and intensity.
\item Joint paper accepted for presentation at Joint Statistical Meetings 2022, Washington D.C.
\end{itemize}}}

\clearpage

\section{Education}
\customcventry{02/2024 ‐ Present}{{\color{blue}\href{https://www.anu.edu.au/}{(Australian National University)}}}{Master of Intl. and Dev. Economics,}{Canberra, ACT}{}{
Relevant topics: Microeconomic policy - Econometrics and modelling - Game theory and competition - Static and dynamic optimization - Development policy
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Explored and built accelerated Computable General Equilibrium (CGE) models using state-of-the-art optimizers and solvers
\item Gained practical experience and a theoretical understanding of experimental and quasiexperimental methods to evaluate policy impacts.
\end{itemize}}
}

\customcventry{02/2023 ‐ 12/2023}{{\color{blue}\href{https://www.anu.edu.au/}{(Australian National University)}}}{Bachelor of Applied Data Analytics,}{Canberra, ACT}{}{
Relevant topics: Demographic cohort analysis - Regression modelling - Social network analysis - Data wrangling and mining
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Built microsimulation models to analyze spatial distribution of impacts of Stage-3 tax cuts across Australia.
\item Classified and studied the behavior of suspected state-backed troll accounts on Reddit using state-of-the-art neural network classifiers and graph analysis.
% \item GPA: 5.875/7 – Semester 1 \& 2
\end{itemize}}}

 \customcventry{Spring 2022}{{\color{blue}\href{https://www.pon.harvard.edu/}{(Harvard Law School)}}}{Mediation and Conflict Management,}{Remote}{}{
 Relevant topics: Negotiation and mediation - Conflict resolution
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Gained hands-on experience in conflict mediation through classroom simulations and case study analyses
\end{itemize}}
 }

\customcventry{02/2022 - 08/2022}{{\color{blue}\href{https://micromasters.mit.edu/dedp/}{(MIT - JPAL)}}}{Data, Economics, and Development Policy - MicroMasters,}{Remote}{}{
Relevant topics: Microeconomics - Econometrics - Qualitative analysis - Survey design - Development policy - Research ethics
}

\customcventry{08/2020 ‐ 12/2022}{{\color{blue}\href{https://www.amrita.edu/}{(Amrita Vishwa Vidyapeetham)}}}{Integ. MSc. Data Science,}{Coimbatore, TN}{}{
Relevant topics: Statistical modelling - Database management and design - Cryptography - Optimization - Real analysis - Linear algebra
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Transferred to ANU seeking a more policy-focused program.
% \item GPA: 8.55/10 – Semester 1 - 5
\end{itemize}}}

\section{Other Courses}
{\begin{itemize}[label=\textbullet]
    \item International Political Economy of Decarbonization - Harvard DCE
    \item Monetary Policy Analysis and Forecasting – International Monetary Fund (IMFx)
    % \item  – Program on Negotiation, Harvard Law School
    \item Effective Leadership through Emotional Intelligence – University of Oxford (Online)
    \item MicroMasters in Entrepreneurship – Indian Institute of Management, Bangalore (IIMBx)

  \end{itemize}}

\section{Skills}
{\begin{itemize}[label=\textbullet]
\item {\textbf{Languages/Frameworks:} Python, Julia, MATLAB, R, Stata, Power BI, Excel}
\item Econometric analysis
\item Simulations and Modelling
\item Data Wrangling and Mining, Pipelining and Management, Visualization and Communication
\item Neural Networks and Deep Learning
\item Natural Language Processing
\end{itemize}}

\section{Languages}
\begin{multicols}{2}
    \begin{itemize}[label=\textbullet]
    \item \textbf{English} [Native]
    \item {\textbf{French} [Basic] - Learning}
    \item {\textbf{Hindi} [Basic]}
    \end{itemize}
\end{multicols}
\end{document}