\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage{amssymb}
\name{Sreehari}{FUCKING Pulickamadhom Sreedhar}
\newcommand*{\mycomment}[1]{}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-8mm}
\begin{center}\textbf{Policy Analysis and Economics}\end{center}
\begin{center}
\begin{tabular}{ c c c }
\faMobile\enspace +61 450087293 & \enspace\enspace\faEnvelope\enspace\enspace spulickamadhom@gmail.com \enspace\faEnvelopeSquare\enspace\enspace u7322074@anu.edu.au & \enspace\enspace\faHome\enspace Canberra, ACT
\end{tabular} \\
\begin{tabular}{c c}
\faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/sreehari-sreedhar/}{in/sreehari-sreedhar} &
\enspace\enspace\faGithub\enspace \color{blue} \href{https://github.com/orectique}{github.com/orectique}
\end{tabular}
\end{center}

\section{Profile}
{Data-driven policy analyst with expertise in microsimulation and economic modeling, focused on delivering actionable insights for complex policy challenges.}

\section{Areas of Expertise}
{Agent-Based Modelling - Policy Analysis - Microsimulation - Negotiation and Mediation - Statistical Analysis and Modelling - Machine Learning}

\section{Professional Experience}
\customcventry{06/2024 ‐ Present}{{\color{blue}\href{https://alga.com.au/}{(Australian Local Government Association)}}}{Modeller - Junior Policy Advisor,}{Canberra, ACT}{}{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]  
\item Developed a centralized knowledge base of data at the council level streamlining policy analysis for local governments.
\item Designed and maintained small-area microsimulation models, enabling estimation of the impact of various policies to councils, with greater precision.
\item Delivered rapid, targeted analyses for Policy Directors on welfare, climate adaptation, and Commonwealth grants, supporting strategic decision-making.
\end{itemize}}

\customcventry{09/2023 ‐ 12/2023}{{\color{blue}\href{https://mandalapartners.com/}{(Mandala Partners)}}}{Research Intern,}{Canberra, ACT}{}{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Synthesized comparative policy research to clarify the impact of federalism across Australian states and territories, informing client recommendations.
\item Engineered robust indicators for quality of life, education, and healthcare using multifactor statistical modeling, enhancing the depth of policy analysis.
\end{itemize}}

\customcventry{07/2023 ‐ 12/2023}{{\color{blue}\href{https://quantecon.org/}{(QuantEcon@ANU)}}}{Research Assistant,}{Canberra, ACT}{}{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Applied high-performance computing and dynamic programming to solve classical economics problems, increasing research efficiency and accuracy.
\item Co-authored and reviewed QuantEcon lecture materials with leading professors, elevating the quality and reach of the educational platform.
\item Led a workshop on multidimensional weighting and constrained sampling for spatial microsimulation, boosting participant proficiency in economic modeling.
\end{itemize}}

\customcventry{10/2021 ‐ 05/2022}{{\color{blue}\href{https://www.amrita.edu/}{(Amrita Vishwa Vidyapeetham)}}}{Lead Data Analyst,}{Coimbatore, TN}{}{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Analyzed large-scale sociological survey data for a joint government-university project, delivering actionable findings for project recommendations.
\item Built an intuitive geospatial data analysis tool for non-technical social scientists, increasing adoption and usability among field researchers.
\item Developed and delivered workshops on ethical data usage and deidentification, improving data integrity and compliance across research teams.
\end{itemize}}

\customcventry{04/2021 ‐ 06/2021}{{\color{blue}\href{https://math.mit.edu/directory/profile.html?pid=1521}{(Dr. Peter J. Kempthorne, MIT)}}}{Research Intern,}{Remote}{}{
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Conducted spatial analysis and aggregation of ACLED social unrest data, revealing key trends in protest frequency for academic publication.
\item Developed new metrics for unrest severity using perceived violence and latent intensity, enabling more nuanced mapping and comparison of unrest periods.
\item Co-authored paper accepted for presentation at Joint Statistical Meetings 2022.
\end{itemize}}

\clearpage

\section{Education}
\customcventry{02/2024 ‐ Present}{{\color{blue}\href{https://www.anu.edu.au/}{(Australian National University)}}}{Master of Intl. and Dev. Economics,}{Canberra, ACT}{}{
Relevant topics: Microeconomic policy - Econometrics and modelling - Game theory and competition - Static and dynamic optimization - Development policy
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Developed and implemented accelerated CGE models with state-of-the-art optimizers, enhancing the analysis of complex economic scenarios.
\item Applied experimental and quasi-experimental methods in coursework and research, strengthening proficiency in policy evaluation and impact assessment.
\end{itemize}}

\customcventry{02/2023 ‐ 12/2023}{{\color{blue}\href{https://www.anu.edu.au/}{(Australian National University)}}}{Bachelor of Applied Data Analytics,}{Canberra, ACT}{}{
Relevant topics: Demographic cohort analysis - Regression modelling - Social network analysis - Data wrangling and mining
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Built and validated microsimulation models to analyze the spatial distribution of Stage-3 tax cut impacts, providing insights into regional disparities.
\item Used neural network classifiers and graph analysis to study suspected state-backed troll accounts on Reddit, contributing to the understanding of online manipulation.
% \item GPA: 5.875/7 – Semester 1 \& 2
\end{itemize}}

\customcventry{Spring 2022}{{\color{blue}\href{https://www.pon.harvard.edu/}{(Harvard Law School)}}}{Mediation and Conflict Management,}{Remote}{}{
 Relevant topics: Negotiation and mediation - Conflict resolution
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Engaged in classroom simulations and case study analyses, developing effective negotiation and conflict resolution skills.
\end{itemize}}

\customcventry{02/2022 - 08/2022}{{\color{blue}\href{https://micromasters.mit.edu/dedp/}{(MIT - JPAL)}}}{Data, Economics, and Development Policy - MicroMasters,}{Remote}{}{
Relevant topics: Microeconomics - Econometrics - Qualitative analysis - Survey design - Development policy - Research ethics
}
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Completed rigorous coursework in microeconomics, econometrics, and development policy, with a focus on evidence-based approaches to global challenges.
\item Applied quantitative and qualitative methods to analyze real-world development interventions, emphasizing research ethics and effective survey design.
\end{itemize}

\customcventry{08/2020 ‐ 12/2022}{{\color{blue}\href{https://www.amrita.edu/}{(Amrita Vishwa Vidyapeetham)}}}{Integ. MSc. Data Science,}{Coimbatore, TN}{}{
Relevant topics: Statistical modelling - Database management and design - Cryptography - Optimization - Real analysis - Linear algebra
\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Developed a strong foundation in statistical modeling, database management, and optimization, applying these skills to real-world data science projects.
\item Collaborated on interdisciplinary research, leveraging advanced analytical techniques to address complex problems in cryptography and data analysis.
\item Transferred to ANU for a more policy-focused curriculum, aligning academic trajectory with career goals in policy analysis.
% \item GPA: 8.55/10 – Semester 1 - 5
\end{itemize}}

\section{Other Courses}
{\begin{itemize}[label=\textbullet]
    \item International Political Economy of Decarbonization - Harvard DCE
    \item Monetary Policy Analysis and Forecasting – International Monetary Fund (IMFx)
    % \item  – Program on Negotiation, Harvard Law School
    \item Effective Leadership through Emotional Intelligence – University of Oxford (Online)
    \item MicroMasters in Entrepreneurship – Indian Institute of Management, Bangalore (IIMBx)

  \end{itemize}}

\section{Skills}
{\begin{itemize}[label=\textbullet]
\item {\textbf{Languages/Frameworks:} Python, Julia, MATLAB, R, Stata, Power BI, Excel}
\item Simulation, Econometric Modelling, and Analysis
\item Data Wrangling and Mining, Pipelining and Management, Visualization and Communication
\item Neural Networks and Deep Learning
\item Natural Language Processing
\end{itemize}}

\mycomment{
\section{Languages}
\begin{multicols}{2}
    \begin{itemize}[label=\textbullet]
    \item \textbf{English} [Native]
    \item {\textbf{French} [Basic] - Learning}
    \item {\textbf{Hindi} [Basic]}
    \end{itemize}
\end{multicols}}

\end{document}